From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-08 papers/ACL2020/analysis.tex
some text in Section 5

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll||rr|rrr}
\toprule
&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
                         model &  gt &  hit &  valid &  human-like &  related &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
        \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
         \midrule
     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
    ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
\bottomrule
\end{tabular}

@@

\paragraph{Alternative Name Prediction}
\begin{figure}
	\centering
	\includegraphics[scale=.2]{images/2323938.jpg}
	\includegraphics[scale=.2]{images/2322259.jpg}
	\includegraphics[scale=.2]{images/2371657.jpg}

@@

\cs{TODO::}
Categorization of "errors" (see Figure~\ref{fig:mistakes}):
\begin{enumerate}
	\item Clear mistake \\
	e.g.,\ rice vs. bread
	\item Alternative name\\
	e.g.,\ building vs. house
	\item Alternative object \cs{(other cluster from verif data)}
	\item Synonym\\
	e.g.,\ plane vs. airplane
	\item Semantically related\\
	e.g.,\  motorcycle vs. scooter
\end{enumerate}

\paragraph{Human Object Naming through Transfer-Learning} Figure \ref{fig:exp_confusions} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600). For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name. Observations:
\begin{itemize}
	\item Retraining faster-rcnn on fewer, entry-level names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
	\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit. Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.  (top right matrix)
	\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits. This is less the case when ResNet is finetuned on VG annotations.
	\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
\end{itemize}

\subsection{[TBC] Humans vs. Models: Which Mistakes do they Make?}
\label{sect:exp_analysis}

\paragraph{Categorization of Errors}
see Figure\ ref{fig:mistakes}
\begin{enumerate}
	\item Clear mistake \\
	e.g.,\ rice vs. bread
	\item Alternative name\\
	e.g.,\ building vs. house
	\item Alternative object \cs{(other cluster from verif data)}
	\item Synonym\\
	e.g.,\ plane vs. airplane
	\item Semantically related\\
	e.g.,\  motorcycle vs. scooter
\end{enumerate}

	\caption{resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:matrices}}
\end{figure}

\subsection{Results}

\paragraph{Overview}
Table\ \ref{tab:exp_overview_results}: \cs{Shows the overview and what MN adds without going into detail: Standard evaluation -- hit; We can additionally distinguish between correct (name alternative, see caption of Table) and clear mistake.}

\paragraph{How do predictions change?} Figure \ref{fig:matrices} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600). For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name. Observations:
\begin{itemize}
\item Retraining faster-rcnn on less names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit. Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.  (top right matrix)
\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits. This is less the case when ResNet is finetuned on VG annotations.
\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
\end{itemize}

\paragraph{Correct predictions}
Table\ \ref{tab:exp_details_correct}: \cs{Gives detailed results to the categories of "correct name" (but not hit): same cluster, WordNet synonym, WordNet hypernym/hyponym}\\
To look into in detail (example images): 
\begin{itemize}
	\item Compare FRCNN vs. FRCNN-finetuned (row block 1 vs. row block 2) with respect to the synonym categories (i.e., predicted name is in a synonym/synonyms\_cluster-relation to the target object) vs. same\_cluster (i.e., predicted name is in response set). 
\end{itemize}

\paragraph{Wrong predictions}

Table\ \ref{tab:exp_details_wrong}: \cs{Gives detailed results to the categories of predicted name\ $\hat{n}$ is incorrect: WordNet co-hyponyms,  other object (inadequacy types: visual, linguistic, bounding box, other (types other+None), $\text{count}(\hat{n})<2$, error (just wrong+unkn(not found in WordNet))}

>>>>

\paragraph{Error Categories} We categorize model predictions into the following types (also see Figure~\ref{fig:mistakes} for examples):

\begin{itemize}
\item Correct-hit: the entry-level name 
\item Correct-valid: a name from the set of valid alternatives, a synonym or a hypernym (\textit{house/building})
\item: Incorrect-human-like: a name produced by annotators, but not a valid alternative of the entry-level name  (\textit{chair/cat})
\item Incorrect-related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
\item Incorrect-off: a non-sensical name (none of the above)
\end{itemize}

\subsection{How human-like are model predictions and errors?}

Table \ref{tab:humanlike} shows the breakdown of the model results for the error categories explained above. An important general trend is that the proportion of human-like error seems to be surprisingly constant across all models. \sz{why??}
Both object detection models essentially achieve the same portion of valid predictions. Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the models makes more nonsensical errors, which might be an effect of the reduction in training data.
Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but less valid predictions, and also less nonsensical errors as compared to FRCNN$_{\text{VG1600}}$.
This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit by the finetuned classification model.
All ResNet models produce a lot of errors in the ``related'' category, which suggests that they tend to confuse similar names that are, however, not valid.

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll||rr|rrr}
\toprule
&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
                         model &  gt &  hit &  valid &  human-like &  related &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
        \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
         \midrule
     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
\bottomrule
\end{tabular}

@@

@@

\subsection{How do predictions correlate with human agreement?}

An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans \sz{is it okay to claim this?}.
In Table \ref{tab:exp_errors_agreement}, we show the break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name. 
Here, we find a very clear pattern for all models, namely that the portion of hits is generally high when human agreement is also high.
Note that this even holds for the ResNet-based classifiers that generally achieve less accuracy.
When agreement is lower, all models produce less hits and more valid alternatives. 
This indicates that there is indeed a certain similarity between what is difficult for humans and models.
Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. \sz{why???}

%\cs{TODO::}
%Categorization of "errors" ():
%\begin{enumerate}
%	\item Clear mistake \\
%	e.g.,\ rice vs. bread
%	\item Alternative name\\
%	e.g.,\ building vs. house
%	\item Alternative object \cs{(other cluster from verif data)}
%	\item Synonym\\
%	e.g.,\ plane vs. airplane
%	\item Semantically related\\
%	e.g.,\  motorcycle vs. scooter
%\end{enumerate}
